Declarative runtime reconfiguration of pulverised distributed systems \thanks{Identify applicable funding agency here. If none, delete this.}

### 2023-05-10 paper-2023-acsos-pulverization.tex
Add metrics

\lstinputlisting[
    float=ht,
    language=Kotlin,
    caption={TODO},
    label=lst:system-configuration,
]{listings/SystemConfig.kt}

@@

\lstinputlisting[
    float=ht,
    language=Kotlin,
    caption={TODO},
    label=lst:runtime-configuration,
]{listings/RuntimeConfig.kt}

\lstinputlisting[
    float=ht,
    language=Kotlin,
    caption={TODO},
    label=lst:reconfiguration-events,
]{listings/ReconfigurationEvents.kt}

@@

>>>>

\lstinputlisting[
    float=ht,
    language=Kotlin,
    caption={
        Example of the usage of the domain-specific language for the system configuration.
        The example configures two types of devices, and for each device defines the components that compose it and which capabilities requires for the execution.
    },
    label=lst:system-configuration,
]{listings/SystemConfig.kt}

@@

\lstinputlisting[
    float=ht,
    language=Kotlin,
    caption={
        Example of the usage of the domain-specific language for the runtime configuration.
        The example defines the runtime configuration of the system, specifying the initial deployment and the reconfiguration rules.
    },
    label=lst:runtime-configuration,
]{listings/RuntimeConfig.kt}

A \texttt{ReconfigurationEvent} is characterized by the \emph{events}
that it produces and the \emph{condition} that must be satisfied to trigger the reconfiguration.
%
The \emph{events} are represented as an asyncronous stream of valued produced by the device and the
\emph{condition} is a predicate that is evaluated on the stream of events.
%
At the first match of the condition, the reconfiguration is triggered and the system is reconfigured with the new deployment.
%
The~\Cref{lst:reconfiguration-events} shows an example of the definition of a reconfiguration event.

\lstinputlisting[
    float=ht,
    language=Kotlin,
    caption={Example of the definition of a reconfiguration event.},
    label=lst:reconfiguration-events,
]{listings/ReconfigurationEvents.kt}

@@

The pulverization approach tries to solve the problem of the deployment independence of the system, in heterogeneous infrastructures.
%
The dynamic reconfiguration of the system is a key point to achieve flexibility and adaptability of the system on the requirements changing.
%
In this section are presented two case studies that show the effectiveness of the approach:
the first case study shows the operation of the framework in a small-scale scenario, while the second case study simulate a large-scale scenario
using the framework in a simulated environment showing the effectiveness of the approach in many different conditions.

\subsection{Metrics}
\meta{descrizione}

As follow are reported the free variables used in the evaluation:
\begin{itemize}
    \item let $n$ be the number of devices;
    \item let $t_d$ be the discharge time of the battery of the devices;
    \item let $B_l$ be the low battery threshold;
    \item let $B_h$ be the high battery threshold;
    \item let $EPI_{cloud}$ be the energy per instruction of the cloud;
    \item let $EPI_{ratio}$ be the ratio of the consumption of the cloud and the device;
\end{itemize}

From the variables above are derived the following metrics:

\begin{itemize}
    \item let $\beta_{device}$ be the number of \emph{behaviour} executed in the device;
    \item let $\beta_{cloud}$ be the number of \emph{behaviour} executed in the cloud;
    \item let $C_{\%}$ be the average battery percentage of the devices;
    \item let $P_{devices}$ be the consumed power of the devices;
    \item let $P_{cloud}$ be the consumed power of the cloud;
    \item let $P_{total}$ be the total consumed power of the system;
    \item let $I_{cloud}$ be the number of server instances of the cloud;
    \item let $\$_{cloud}$ be the cost of the cloud; 
\end{itemize}
